---
title: "Tutorial: H2020 proposal (with Nextcloud)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Tutorial: H2020 proposal (with Nextcloud)}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(kwb.budget)
```

## Set environment variables for Nextcloud access

Provide the URL to your Nextcloud instance in environment variable 
`NEXTCLOUD_URL`.

On Nextcloud, create a password for an application to login:

- Go to `<NEXTCLOUD_URL>/index.php/settings/user/security`
- In section "Devices and sessions"
    - Enter a name (e.g. "rstudio") in the text field "App name",
    - press the button "Create new app password" and
    - note the user name and the generated password.

Provide user name and password as retrieved above to environment variables 
`NEXTCLOUD_USER` and `NEXTCLOUD_PASSWORD`, respectively.

## List files on Nextcloud

```{r}
nextcloud_files <- kwb.nextcloud::list_files(
  path = "proposals_external/2024_EU_Twin_Transition/20_stage_2/60_budget", 
  full_info = TRUE
)

nextcloud_files$file
```

## Download files from Nextcloud

```{r}
local_files <- kwb.nextcloud::download_files(hrefs = nextcloud_files$href)

local_files
```

## Read (local) budget file 

```{r}
budget <- kwb.budget::read_partner_budget_from_excel(file = local_files[1L])

str(budget, give.attr = FALSE)
```

The details are returned as attributes:

```{r}
get_details <- function(name) {
  details <- kwb.utils::getAttribute(budget, name)
  is_complete <- !is.na(details$wp)
  details[is_complete, ]
}

get_details("personnel")
get_details(name = "consumables")
get_details("equipment")
get_details("subcontracting")
```

## Read a set of (local) budget files

```{r}
budgets <- kwb.budget::read_partners_budget_from_excel(
  files = local_files
)
```

If errors occur, switch off parallel processing and hope for clear error 
messages:

```{r}
budgets <- kwb.budget::read_partners_budget_from_excel(
  files = local_files, 
  run_parallel = FALSE
)
```

<!-- 

**To do:** 

- Add example from **R/.read_budget_files.R** after moving functions in 
own file under **R/..**

- Maybe also add environment variables NEXTCLOUD_URL/USER/PASSWORD to travis-ci.org 
in order to do have an working example (but with anomynised data !!!)

-->
